---
title: "simpleschoolsR"
author: "Zach Timpe"
date: "10-18-2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simpleschoolsR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo=TRUE,
  include=TRUE
)
```

```{r setup}
library(simpleschoolsR)
```
The purpose of this package is to ease the buren of cleaning and preparing school
names and addresses for tidy presentation and use in the event that matching
is needed. This short vignette provides a case example of using the first function
of this package, **clean_schools**, to convert a column of school names to title
case, and create a new column prepared for potential matching.

# Clean school names
```{r}
test_df <- data.frame(schools=c("Paola High School", "Louisburg High School", 
                "osawatomie high", "prarie view high school"))
```
To utilize the clean_schools function, specify the name of the data frame and the
column you wish to clean. Don't forget that you need to specify a list of terms to replace, along with their
replacements!
```{r}
strings <- simpleschoolsR::school_strings()
```
```{r}
simpleschoolsR::clean_schools(test_df,schools,strings)
```
